Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-19 sections/pitfalls.tex
Update pitfalls.tex
Typo-correction

Due to the increased horizontal resolution, even the $x,y$-alignment of SICM
pipette and the laser beams becomes more challenging since the tolerable
offset between the two decreases. While it has been reported that fine
adjustment screws are sufficient to align the pipette and the beam in the
combination of SICM and confocal microscopes \cite{Gorelik2002a,
  Shevchuk2008,Novak2014}, additional piezo actors might be required for the
alignment of STED and SICM. However, for the alignment of the SICM pipette and a
confocal beam by piezo actors a remaining offset in the alignement has been
reported \cite{Bednarska2020}.

>>>>

Due to the increased horizontal resolution, even the $x,y$-alignment of SICM
pipette and the laser beams becomes more challenging since the tolerable
offset between the two decreases. While it has been reported that fine
adjustment screws are sufficient to align the pipette and the beam in the
combination of SICM and confocal microscopes \cite{Gorelik2002a,
  Shevchuk2008,Novak2014}, additional piezo actors might be required for the
alignment of STED and SICM. However, for the alignment of the SICM pipette and a
confocal beam by piezo actors a remaining offset in the alignment has been
reported \cite{Bednarska2020}.
